The \Rpackage{eisa} and \Rpackage{biclust} packages

### 2011-10-18 eisa/inst/doc/EISA_biclust.Rnw
eisa: tutorials use 'xlib' graphics, if available.
Updated a vignette because of the new biclust package.

Now we will convert the \Rclass{Biclust} object to an \Rclass{ISAModules} 
object, that is used in the \Rpackage{eisa} package. To help
some \Rpackage{eisa} functions, we add the name of the annotation package to 
the parameters stored in the \Rclass{Biclust} object, this is always advised.
The procedure makes use of the probe and sample names that are kept and stored 
in the \Rclass{Biclust} object, this information will be used later, e.g. for 
the enrichment analysis. The conversion itself can be performed with
the usual \Rfunction{as} function. 
<<convert bc to isa>>=
Bc@Parameters$annotation <- annotation(ALL.filtered)
modules <- as(Bc, "ISAModules")
modules
@

>>>>

Now we will convert the \Rclass{Biclust} object to an \Rclass{ISAModules} 
object, that is used in the \Rpackage{eisa} package. To help
some \Rpackage{eisa} functions, we add the name of the annotation package to 
the parameters stored in the \Rclass{Biclust} object, this is always advised.
We also need to add the input data to the \Rclass{Biclust} object by
hand, as this is not included in the \Rclass{Biclust} object, when
using a recent version of the \Rpackage{biclust} package. The column
and row names of the data will be used later, e.g. for the enrichment
analysis. The conversion itself can be performed with the usual
\Rfunction{as} function.  
<<convert bc to isa>>=
Bc@Parameters$annotation <- annotation(ALL.filtered)
Bc@Parameters$Data <- exprs(ALL.filtered)
modules <- as(Bc, "ISAModules")
modules
@
